Technical Report

### 2024-04-30 Reports/tech_report1.tex
update report

>>>>

\section{Nodes chosen method comparison tests}

The date is 2024 04 30 (and some days before).

We do two parts of test: one is for only considering length 3 paths, for layer 3 and 5. Another is considering length 3 and 4 paths, for layer 5.

For part1, there is no parameter. And for part2, there is a parameter (let us call it $r$) when comparing values of nodes in layer 1 and layer 3.
